---
title: "Map Basics Assignment"
author: "T. G. Walker"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
library(ggplot2)
library(MASS)
library(gridExtra)
library(adehabitatHR)
library(OpenStreetMap)
library(rgeos)
library(ggfortify)
library(sp)
library(ks)
library(raster)


pacman::p_load("ggsn","leaflet","mapdata","maptools","OpenStreetMap","rgdal","tidyverse")
```
## Static Map

First is my static map, which is my study area from my thesis that shows the 26 sites I collected data from and are labeled with site names and their points are colored by Visual assesment scores.


```{r Static Map, echo=TRUE}
mapdata <- read.csv("Bat_Map_Data_2021.csv")


mapdata$lat<-as.numeric(mapdata$lat)
mapdata$lon<-as.numeric(mapdata$lon)

max(mapdata$lat, na.rm=T)
max(mapdata$lon)
mapdata_raster <- openmap(c(max(mapdata$lat)+0.010, min(mapdata$lon)-0.010), + 
                            c(min(mapdata$lat)-0.010, max(mapdata$lon)+0.010), type = "bing")


mapdata_raster_proj <- openproj(mapdata_raster, projection = "+proj=longlat +datum=WGS84")


autoplot.OpenStreetMap(mapdata_raster_proj, expand = TRUE) + geom_point(data=mapdata, aes(lon, lat)) +
  geom_point(data = mapdata, aes(lon, lat), size = 3.0) + aes(color = Visual_Score) +
  geom_text(data=mapdata,aes(x=lon,y=lat,label=Site_ID), color="white", vjust=-0.60, size=4.01, fontface="bold")+
  theme(axis.title = element_text(face="bold")) + labs(x="Longitude", y="Latitude") +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) + theme_bw()+
  north(mapdata, location = "bottomleft", scale = 0.15, symbol = 4, anchor = c(x= -87.15, y= 36.55)) + 
  scalebar(mapdata, dist = 2, dist_unit = "mi", transform = TRUE, model = "WGS84", location = "bottomleft", st.dist = 0.05, st.size = 1, anchor = c(x=-87.8,y=36.55)) +
  annotate("text", x = -87.6, y = 36.56, label = "Trevor Walker\n October2021", size = 3.5, color="white")+
  labs(title = "Fort Campbell Kentucky/Tennessee")
```

## Interactive Map

Next Up is my Interactive Map.

I used data collected by most of you in this class from Dr. Woltmans Ornithology project this year however this map shows circle points that are correlated by size to numbers of individual birds that were spotted across campus.

The points can also be scrolled over to show what species of bird was being recorded of the four listed here:

NOMO- Northern Mockingbird

EABL- Eastern Bluebird

HOSP- House Sparrow

EUST- European Starling

```{r Interactive Map, echo=TRUE}
alldata <- read.csv("2020data.csv")

pal <- colorNumeric(
  palette = "RdBu",
  domain = alldata$Indivs.)


leaflet(alldata) %>% 
  addTiles() %>% 
  addWMSTiles("https://basemap.nationalmap.gov/arcgis/services/USGSTopo/MapServer/WmsServer", layers = "0")%>%
  addScaleBar()%>%
addCircleMarkers(data = alldata,
                 popup = alldata$Species,
                 color = ~pal(alldata$Indivs.),
                 radius = ~sqrt(Indivs.), group = 'Species - Indivs.')%>%
  addLegend("bottomright", pal = pal, values = ~Indivs.,
            title = "bird #'s",
            labFormat = labelFormat(prefix = ""),
            opacity = 1)
```


